---
title: "Lab 9"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE,  
                      warning = FALSE, message = FALSE, 
                      fig.align = "center",
                      R.options = list(max.print=100))

# Edit the file starting below
```

### Enter the names of the group members here:

**This assignment is due by the end of the day. Only one student in the group submits a pdf file on Gradescope.**

*For all questions, include the R commands/functions that you used to find your answer (show R chunk). Answers without supporting code will not receive credit. Write full sentences to describe your findings.*

Let's load the appropriate packages for today:

```{r, warning=FALSE}
library(tidyverse)
```

The dataset for this lab contains information about the chances of admissions into graduate school:

```{r}
# Upload data from GitHub
admissions <- read_csv("https://raw.githubusercontent.com/laylaguyot/datasets/main//Admission_Predict.csv") |>
  # Rename variables for easier manipulation 
  rename(GRE_Score = `GRE Score`, TOEFL_Score = `TOEFL Score`,
         University_Rating = `University Rating`, Admission_Chance = `Chance of Admit`)

# Look at a sample of this data
admissions |>
  sample_n(size = 10)
```

This dataset contains the following variables: GRE Scores (out of 340), TOEFL Scores (out of 120), 
University Rating (out of 5), Statement of Purpose (`SOP`) and Letter of Recommendation (`LOR`) Strength (out of 5), Undergraduate GPA (out of 10), Research Experience (either 0 or 1), Chance of Admission (ranging from 0 to 1).

The goal of the lab is to make predictions for graduate admission based on other features of a student's application.

------------------------------------------------------------------------

### Question 1: (2 pts)

Pick one variable to predict a student's `Admission_Chance`. What potential relationship between this variable and a student's `Admission_Chance` do you anticipate? Answer that question before exploring the data!

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 2: (4 pts)

Visualize the relationship between the predictor you chose in the previous question and the response variable. Does your visualization match the relationship that you had anticipated?

```{r}
# your code goes below (make sure to edit comment)

```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 3: (4 pts)

Fit a linear regression model to predict a student's `Admission_Chance` based on the predictor you chose in the first question. Write the expression of the linear model and report the performance of this model.

```{r}
# your code goes below (make sure to edit comment)

```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 4: (4 pts)

Now choose two other predictors to estimate a student's `Admission_Chance`. Visualize the relationship between each predictor you just chose and the response variable. Does there appear to be a relationship between each predictor and the response variable?

```{r}
# your code goes below (make sure to edit comment)

```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 5: (4 pts)

Fit a linear regression model to predict a student's `Admission_Chance` based on the two predictors you chose in the previous question. Is this model better than the one with one predictor? Why or why not?

```{r}
# your code goes below (make sure to edit comment)

```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Formatting: (2 pts)

Comment your code, write full sentences, knit your file, and select all appropriate pages in Gradescope for each question!
